---
title: "ANA 515 Week5 Assignment"
author: Kohei Nishitani
output: 
  html_document:
    theme: flatly
---

```{r libs, include=FALSE}
library(bslib)
library(knitr)
library(tidyverse)
library(readr)
library(ggplot2)
library(scales)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

```


```{r setup, include=FALSE}
setwd("D:/Workspace/McDaniel-Repository/515/week5")

housing_data <- read.csv("kc_house_data.csv")

housing_data$grade <- as.factor(housing_data$grade)
```

## Intro
This [dataset originates from King County, WA, USA](https://www.kaggle.com/datasets/harlfoxem/housesalesprediction/data), contains a wide range of real estate sales data which is comprehensive details on homes sold within the county, featuring over 20 columns that captures various aspects of the properties listed. 


## Takeaway1
This dataset has `r nrow(housing_data)` sales transactions with `r ncol(housing_data)` variables. The mean sales price is `r format(mean(housing_data$price), big.mark = ",", scientific = FALSE)`. Given this histogram and this mean value, we see the skewness of the distribution.

```{r plot, echo=FALSE}
ggplot(data = housing_data, aes(x = price))+
  geom_histogram(binwidth = 100000)+
  scale_x_continuous(labels = label_comma())

```

## Takeaway2
To get more in-depth insights, I visualize the relationship between price, sqft and housing grade index. The first scatter plot shows the positive correlation between price and sqft; however we can't find a explicit insight about grade due to overwrap. As a next step, I added facet and visualize with multiple charts. It helped me to grasp how grade also affects to price.   


```{r plot1, echo=FALSE}
ggplot(data = housing_data, aes(x = sqft_living, y = price))+
  geom_point()+
  geom_jitter(aes(colour = grade))+
  scale_x_log10() + 
  scale_y_log10() 

```


```{r plot2, echo=FALSE}
ggplot(data = housing_data, aes(x = sqft_living, y = price))+
  geom_point()+
  geom_jitter(aes(colour = grade))+
  scale_x_log10() + 
  scale_y_log10() 
  facet_wrap(~ grade)
```
